The Role of Variability in Learning Generalization: A Computational Modeling Approach

### 2024-05-26 Presentation/slides.qmd
add task vids to slides

---
title: "The Role of Variability in Learning Generalization: A Computational Modeling Approach"
subtitle: "Dissertation Defense"
format: 
  html: default
    #toc: true
    #shift-heading-level-by: 1
    #toc-expand: true
  clean-revealjs:
    #theme: moon #white
    #output-ext: revealjs.html
    output-file: slides_revealjs
    slideNumber: true
    hash-type: number # Use slide numbers in the URL hash
    center: true
    scrollable: true
    chalkboard:
      theme: whiteboard
  pptx:
    incremental: true
  # hugo-md:
  #   include: false
  #   html-math-method: mathjax
  #   output-file: slides_hugo.md
  gfm:
    output: false
    output-file: slides_gfm.md
author:
  - name: Thomas Gorman
    url: https://tegorman13.github.io
    orcid: 0000-0001-5366-5442
    affiliations:
      - name: Indiana University
        department: Psychological & Brain Sciences, Cognitive Science
params:
  start_slide: 0
#engine: knitr
---

@@

:::: {.columns}
::: {.column width="50%"}
![](assets/methodsFig1.png)
:::

::: {.column width="50%"}
- **Training Stage** - 200 training trials. Constant groups throws from single position. Varied group 60 trials from 2 locations. 
- **Transfer Stage** - All subjects tested from both positions they were trained, and the positions trained by other group
- **Data recorded** - For every throw, recorded the X velocity and Y velocity of ball at release
:::

@@

@@

<!-- create slide with 2 columns and add text -->

>>>>

---
title: "The Role of Variability in Learning Generalization: A Computational Modeling Approach"
subtitle: "Dissertation Defense"
format: 
  html: default
    #toc: true
    #shift-heading-level-by: 1
    #toc-expand: true
  clean-revealjs:
    #theme: moon #white
    #output-ext: revealjs.html
    output-file: slides_revealjs
    slideNumber: true
    hash-type: number # Use slide numbers in the URL hash
    center: true
    scrollable: true
    chalkboard:
      theme: whiteboard
  pptx:
    incremental: true
  hugo-md:
    include: false
    html-math-method: mathjax
    output-file: slides_hugo.md
  gfm:
    output: false
    output-file: slides_gfm.md
author:
  - name: Thomas Gorman
    url: https://tegorman13.github.io
    orcid: 0000-0001-5366-5442
    affiliations:
      - name: Indiana University
        department: Psychological & Brain Sciences, Cognitive Science
params:
  start_slide: 0
#engine: knitr
---

@@

:::: {.columns}
::: {.column width="60%"}
<!-- ![](assets/methodsFig1.png) -->

::: {.content-visible when-format="html"}
![](assets/htt_vid.mov){height="540" loop="true" autoplay="true"}
:::

::: {.content-visible unless-format="html"}
![](assets/methodsFig1.png)
:::

::: {.column width="40%"}
- **Training Stage** - 200 training trials. Constant groups throws from single position. Varied group 60 trials from 2 locations. 
- **Transfer Stage** - All subjects tested from both positions they were trained, and the positions trained by other group
- **Data recorded** - For every throw, recorded the X velocity and Y velocity of ball at release
:::

@@

## Task

<!-- {{< video assets/htw_vid.mov width="720" height="540" >}} -->

::: {.content-visible when-format="html"}
![](assets/htw_vid.mov){height="540" loop="true" autoplay="true"}
:::

::: {.content-visible unless-format="html"}
![](assets/htw_task_fig.png)
:::

@@
